Regional and Urban Economics

### 2023-02-19 Retail Agglomeration_Theory.qmd
...

The study utilize a quantitative research approach, employing spacial explanatory data analysis techniques to determine the location decisions of firms.
Geographical data was collected from locations in Norway showing all dentists, central places, retail agglomeration and other points of interest such as the government regulated wine monopoly.
Spatial regression analyses was used to identify the factors influencing the location decisions of firms.

@@

`A brief description of the problem and its importance CHECK`

`Statement of purpose or what was done`

`A brief description of main results`

`Description of methodology, main challenges and solutions`

`Discretion of the papers contribution in relation to previous research`

`Organization of paper`

>>>>

The study utilize a quantitative research approach, employing spacial explanatory data analysis techniques to determine the location decisions of firms.
Geographical data was collected from locations in Norway showing all dentists, central places, retail agglomeration and other points of interest such as the government regulated wine monopoly.
Combines with regional income data a spatial regression analyses was used to identify the factors influencing the location decisions of firms.

@@
